---
title: 'Monitoring Report'
author: 'Michael Rahija, Research Officer'
date: "`r format(Sys.time(),'%B %d , %Y')`"
output: pdf_document
classoption: landscape
---

 

```{r include=FALSE, cache=FALSE}
library(XLConnect)

sys <- Sys.info()

if(sys[5] == "x86_64"){
  dir = "~/Dropbox/monitorFrame" #Mac
  res.dir = "T:/Team_working_folder/G/11. Research/"
  ta.dir = "T:/Team_working_folder/G/13.Training/"
} else if (sys[5] == "Michael"){
  dir = "C:/Users/Michael/Dropbox/monitorFrame"#HOME PC
  res.dir = "T:/Team_working_folder/G/11. Research/"
} else if (sys[6]=="Rahija") {
  dir = "C:/Users/rahija/Dropbox/monitorFrame" #FAO PC
  res.dir = "T:/Team_working_folder/G/11. Research/"
  ta.dir = "T:/Team_working_folder/G/13.Training/"
} else {
  stop("Implement location for current user!")
}

setwd(dir)

#Source required functions
files = dir(path = paste0(dir, "/R"), full.names = TRUE)
sapply(files, source)

```

# OUTPUT 3: RESEARCH COMPONENT

## 01-FRAM-3-MSCD           
### Service provider: Angela Piersante


```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"01-FRAM-3-MSCD/Monitoring_notebook.xlsx")

overview <- fetch_overview(path = path)
knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 


countries.t <- fetch_countries(path = path)
knitr::kable(countries.t, caption = "Countries", align = "l")  

comments.t <- fetch_comments(path = path)
knitr::kable(comments.t, caption = "Comments", align = "l") 
```

## 03-COLL-1-CostOfProduction          
### Service provider: Sangita's team/ Focal point: Carola Fabi


```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"03-COLL-1-CostOfProduction/Monitoring_notebook.xlsx")

overview <- fetch_overview(path = path)
knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 


countries.t <- fetch_countries(path = path)
knitr::kable(countries.t, caption = "Countries", align = "l")  

comments.t <- fetch_comments(path = path)
knitr::kable(comments.t, caption = "Comments", align = "l") 
```

## 03-COLL-2-PostHarvestLosses          
### Service provider: Kebe / Focal point: Carola Fabi

```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"03-COLL-2-PostHarvestLosses/Monitoring_notebook.xlsx")

overview <- fetch_overview(path = path)
knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 


countries.t <- fetch_countries(path = path)
knitr::kable(countries.t, caption = "Countries", align = "l")  

comments.t <- fetch_comments(path = path)
knitr::kable(comments.t, caption = "Comments", align = "l") 
```


## 03-COLL-3-CAPI        
### Service provider: World Bank/Michael / Focal point: Michael Rahija

```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"03-COLL-3-CAPI/Monitoring_notebook.xlsx")

overview <- fetch_overview(path = path)
knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 


countries.t <- fetch_countries(path = path)
knitr::kable(countries.t, caption = "Countries", align = "l")  

comments.t <- fetch_comments(path = path)
knitr::kable(comments.t, caption = "Comments", align = "l") 
```

## 05-LIVE-1-LivestockAndProducts
### Service provider: Uni of New England / Focal point: Neli

```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"05-LIVE-1-LivestockAndProducts/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```


## 06-FOOD-1-FoodBalanceSheets
### Service provider: ESS / Focal point: ?????

```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"06-FOOD-1-FoodBalanceSheets/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```


## 07-CROP-1&2-AreaYieldProduction           
### Service provider: IASRI / Focal point: Michael Rahija

```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"07-CROP-1&2-AreaYieldProdn-MixedContRepCrops/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 07-CROP-4-HorticulturalCrops         
### Service provider: FAORAF / Focal point: Michael Rahija

```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"07-CROP-4-HorticulturalCrops/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 08-REMO-3-Using-LCLU-Databases           
### Service provider: J. Latham / Focal point: Angela Piersante
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"08-REMO-3-Using-LCLU-Databases/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 09-ADMI-1-Quality&Use-AdminData          
### Service provider: ISU & MU / Focal point: Dramane Bako
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"09-ADMI-1-Quality&Use-AdminData/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 10-FISH-1-AgCensus-Module         
### Service provider: S. Tsuji and J. Gee  / Focal point: Angela Piersante
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"10-FISH-1-AgCensus-Module/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 10-FISH-2-Fisheries-MSF        
### Service provider:  / Focal point: Dramane Bako
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"10-FISH-2-Fisheries-MSF/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```
## 11-FORE-1-ForestryStats         
### Service provider: A. Lebedys & Y. Li / Focal point: Angela Piersante
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"11-FORE-1-ForestryStats/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 11-FORE-2-WoodFuel         
### Service provider: A. Lebedys & Y. Li / Focal point: Angela Piersante
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"11-FORE-2-WoodFuel/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 14-DATA-1-FarmTypology    
### Service provider: Mary Ahearn / Focal point: Neli Georgieva
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"14-DATA-1-FarmTypology/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 14-DATA-2-Reconciling-CensSurv        
### Service provider: FAO-RAF / Focal point: Neli Georgieva
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"14-DATA-2-Reconciling-CensSurv/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 15-SUST-1-Gender        
### Service provider: ESS / Focal point: Chiara Brunelli
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"15-SUST-1-Gender/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```


## 15-SUST-2-Youth       
### Service provider: ?? / Focal point: Michael Rahija
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"15-SUST-2-Youth/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 15-SUST-3-AgriEnviro       
### Service provider: ?? / Focal point: Monica Madrid
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"15-SUST-3-AgriEnviro/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```



## 15-SUST-4-Productivity       
### Service provider: ?? / Focal point: 
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"15-SUST-4-Productivity/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 15-SUST-5-Sustainability       
### Service provider: ?? / Focal point: 
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"15-SUST-5-Sustainability/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

## 16-RURA-1-RuralStats       
### Service provider: ?? / Focal point: Carola Fabi 
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(res.dir,"16-RURA-1-RuralStats/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

countries.t <- fetch_countries(path = path)

knitr::kable(countries.t, caption = "Countries", align = "l") 

comments.t <- fetch_comments(path = path)

knitr::kable(comments.t, caption = "Comments", align = "l")  
```

# OUTPUT 4: TRAINING AND TECHNICAL ASSISTANCE

## CAPI-eLearning      
### Service provider: Consultants / Focal point: Michael Rahija & Carola Fabi 
```{r, echo=FALSE,fig.pos="placeHere"}
path = paste0(ta.dir,"CAPI-eLearning/Monitoring_notebook.xlsx")
overview <- fetch_overview(path = path)


knitr::kable(overview, caption = paste0("Overview - ",
                                        "Updated: ",as.Date(file.mtime(path))),
             align = "l") 

```

##WELCOME TO NEW COLLEAGUES!

